Modal Abstractions for Virtualizing Memory Addresses

### 2024-07-10 examples.tex
start changing specs
+

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m)  \ast \texttt{rbp-8} \mapsto_{\textsf{v}} \textsf{entry} \ast  \texttt{rbp-16} \mapsto_{\textsf{v}} \textsf{next} \ast \texttt{r8}  \mapsto_{\textsf{r}} \textsf{\_} \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{\_}  }_{\rtv}$
$\specline{\mathsf{entry} \in \Xi \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi,m)  \ast \textsf{rbp-8} \mapsto_{\textsf{v}} \textsf{entry} \ast \texttt{r8}  \mapsto_{\textsf{r}} \textsf{\_}  \ast  \texttt{rbp-16} \mapsto_{\textsf{v}} \textsf{next} \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{entry}  }_{\rtv}$
$\specline{ \ulcorner \Xi \;!!\; \mathsf{entry} = \mathsf{Some V} \urcorner \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$

@@

@@

$\specline{\ghostmaptoken{\delta{}s}{\rtv}{\delta} \ast \mathsf{nextpaddr} \in \Xi\setminus \{ \mathsf{entry} \} \} }_{\rtv}$

@@

>>>>

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus\{\textsf{entry}\},m)  \ast \texttt{rbp-8} \mapsto_{\textsf{v}} \textsf{entry} \ast  \texttt{rbp-16} \mapsto_{\textsf{v}} \textsf{next} \ast \texttt{r8}  \mapsto_{\textsf{r}} \textsf{\_} \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{\_}  }_{\rtv}$
$\specline{ \textsf{entry} \mapsto_{\textsf{id}} \textsf{v} \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$

@@

$\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus\{entry\},m)  \ast \textsf{entry}\mapsto_{\textsf{pte,q}}\textsf{entryv} \ast \textsf{rbp-8} \mapsto_{\textsf{v}} \textsf{entry} \ast \texttt{r8}  \mapsto_{\textsf{r}} \textsf{\_}  \ast  \texttt{rbp-16} \mapsto_{\textsf{v}} \textsf{next} \ast \texttt{rdi}  \mapsto_{\textsf{r}} \textsf{entry}  }_{\rtv}$
$\specline{ \textsf{entry} \mapsto_{\textsf{id}} \textsf{v} \ast\urcorner \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$

@@

$\specline{ \textsf{entry} \mapsto_{\textsf{id}} \textsf{v} \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$

@@

$\specline{ \textsf{entry} \mapsto_{\textsf{id}} \textsf{v} \ast \textsf{entry\_val}_{\textsf{pfn}} \mapsto_{\textsf{id}} \textsf{\_} \ast \forall_{i\in \textssf{0 ... 511} } \ldotp  \textsf{entry\_val }_{\textsf{pfn}} + \texstf{i * 8} \mapsto_{\textsf{id}} \textsf{\_}   \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta} \ast \mathsf{nextpaddr} \in \Xi\setminus \{ \mathsf{entry} \} \} }_{\rtv}$

@@

$\specline{ \texttt{rbp-16} \mapsto_{\textsf{v}} \textsf{entry\_val}_{\textsf{pfn}}  \ast \texttt{rax} \mapsto_{\textsf{r}} \textsf{nextpaddr}  }_{\rtv}$
